Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-12-10 paper/main.Rmd
main update

## Choice of parameters of the distribution

Under null distribution

@@

@@

## Parameters of the distribution

>>>>

## Effect of parameters of the distribution under null distribution

@@

**Objective:** 1. Behavior of wpd under different null designs N(0,1), N(5, 1), N(0,5) and N(5,5), Gamma(0,1), Gamma(0, 0.2) for different nx and nfacets. Here, we have to fix a value of lambda = 0.67.

**Assumptions:** There is no difference in distribution between any facet or x-category
nsim = 200
lambda = 0.67

**Questions:** 
- How raw value of wpd changes with different nx and nfacet for different location and scale of a Normal and non-normal distribution

```{r}

```{r}

@@
